\section{Empirical Evaluation}

%Let us present our empirical evaluation on \tool{}'s
%accuracy in localizing faults in Web applications. 

We conducted our empirical evaluation on {\tool}'s accuracy in fault
localization with three subject systems from \code{sourceforge.net}
with the sizes ranging from 19 KLOC to 156KLOC
(Table~\ref{tab:subject-systems}).  \code{AddressBook} is an
application to manage contact information and user
groups. \code{SchoolMate} is a web system for managing students,
teachers, and classes in a school. The largest subject system,
\code{ZenCart}, is an e-commerce application. These subject systems
have been used in prior work on fault detection for Web-based
applications~\cite{icsm13,apollo10}.
%All of these applications have interactions with a database through
%SQL queries.

%%%For each system, the number of SQL queries is shown in the column \code{Query}.

%database-interaction points is shown in the last column \code{DB-I}.

%sub

\input{eval-1}

\subsection{Localizing Faults in SQL's Predicates}

%\subsection{Experiment Setup}

%subject systems table

%%\vspace{0.04in}
%%\noindent {\bf Experiment Setup.}

In this experiment, we conducted two more studies. In our first study,
we used the same single-fault mutants for SQL queries as in the
previous experiment.  Each mutant program contains one single fault in
a predicate of a given SQL query. In our second study, each mutant
contains multiple faults.  In each study, we applied our two
algorithms to localize the seeded faults: (1) \tool{}'s single-fault
algorithm to detect SQL predicate faults assuming that there is a
single fault in the query (Section~\ref{single-fault-section}), and
(2) \tool{}'s multi-fault algorithm to detect SQL predicate faults
with no prior assumption about the number of faults
(Section~\ref{multi-fault-section}). The output of each algorithm is a
ranked list of the predicates in the SQL query, with the
highest-ranked predicate being the most likely one to contain the
fault. To evaluate {\tool}'s accuracy, we counted the number of times
that a faulty predicate appears in the top-ranked list of faulty
predicates returned by {\tool}.

\paragraph{Results on Localizing Single Faults}

%\vspace{0.04in} {\bf A. Results on Localizing Single Faults}

Table~\ref{tab:eval-single-faults} displays the evaluation result of
our single-fault and multi-fault localization algorithms. Column
\code{\#M} gives the number of mutants with single faults for each
system. Under column \code{Single-fault ranks}, the values in the five
sub-columns show the number of times the seeded fault appears in the
first to the fifth position of the resulting ranked list of
\tool{}'s single-fault algorithm.
%%Since the SQL queries that we used in our study have from 2-5
%%predicates, we
Table~\ref{tab:eval-single-faults} shows the top-1 to top-5 results.
In \code{AddressBook}, \tool{} correctly localized 27 out
of the 30 seeded faults with a single recommendation. With a ranked
list of 3 recommendations, it can correctly locate all 30 faults.

%one fault is ranked second in the list and two other faults appear
%in the third position.

\begin{table}[t]
    \centering
    \small
    \caption{Results on Single Seeded Faults in SQL queries}\label{tab:eval-single-faults}
    \setlength{\tabcolsep}{3.7pt}
\begin{tabular}{@{}lcccccccccccc@{}}
    \toprule
        &   & \multicolumn{5}{@{}c@{}}{\textbf{Single-fault ranks}} & & \multicolumn{5}{@{}c@{}}{\textbf{Multi-fault ranks}} \\
    \cmidrule{3-7} \cmidrule{9-13}
    \textbf{Sys.} & \textbf{\#M} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} \\
    \midrule
    AB     & 30     & 27    & 1     & 2     & -     & -     &   & 27    & 1     & 2     & -     & - \\
    SM     & 54     & 43    & 11    & -     & -    & -     &   & 41    & 12    & 1     & -     & - \\
    ZC     & 91     & 77    & 8     & 4     & 2     & -     &   & 77    & 8     & 4     & 2     & - \\
    \midrule
%    \%     &        & 84    & 11    & 3     & 1     & 0     &   & 83    & 12    & 4     & 1     & 0 \\
    \multicolumn{2}{c}{\% coverage}  & 84    & 96    & 99     & 100     & 100     &   & 83    & 95    & 99     & 100     & 100 \\
    \bottomrule
\end{tabular}
\end{table}

Column \code{Multi-fault ranks} (Table~\ref{tab:eval-single-faults})
shows the number of times a fault appears in the corresponding
position in the ranked list of \tool{}'s multi-fault
algorithm.
%As seen, the results are {\em comparable} to those produced by the
%single-fault algorithm.
In \code{SchoolMate}, the single-fault algorithm performed slightly
better than multiple-fault algorithm.
%This is because the multi-fault algorithm does not have the prior
%knowledge that there is only one single fault in the program, while
%the other algorithm is specialized toward single faults.
The last row in Table~\ref{tab:eval-single-faults} (\code{\%
coverage}) shows the percentage the faults that are covered by the
corresponding top-ranked list. Overall, around 84\% of the seeded
faults are correctly identified by \tool{} with a single
recommendation.  The majority of the faults (96\%) can be found in the
top-2 results from two algorithms.

\paragraph{Results on Localizing Multiple Faults}

\begin{table}[t]
    \centering
%    \scriptsize
    \caption{Results on Multiple Seeded Faults in SQL queries}\label{tab:eval-multi-faults}
\begin{tabular}{@{}lcccccccccc@{}}
    \toprule
        &   & \multicolumn{4}{@{}c@{}}{\textbf{Single-fault ranks}} & & \multicolumn{4}{@{}c@{}}{\textbf{Multi-fault ranks}} \\
    \cmidrule{3-6} \cmidrule{8-11}
    \textbf{Sys.} & \textbf{\#M} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} \\
    \midrule
    AB     & 14     & 9     & 3     & 2     & 0     &   & 10     & 2     & 2     & 0 \\
    SM     & 27     & 13    & 12    & 2     & 0     &   & 18     & 8     & 1     & 0 \\
    ZC     & 38     & 19    & 9     & 2     & 8     &   & 19     & 9     & 2     & 8 \\
    \midrule
%    \%     &        & 52    & 30    & 8     & 10    &   & 59    & 24     & 6     & 10 \\
    \multicolumn{2}{c}{\% coverage}  & 52    & 82    & 90     & 100    &   & 60    & 84     & 90     & 100 \\
    \bottomrule
\end{tabular}
\end{table}

To evaluate how well \tool{} performs on multiple seeded faults, we
conducted another study in which we seeded two errors for each
mutant. Table~\ref{tab:eval-multi-faults} shows the results.
% of \tool{}'s fault localization.
The rows and columns are similar to those in
Table~\ref{tab:eval-single-faults} except that column \code{top-1} is
not applicable since there are two errors. We consider that the faults
in a mutant are localized in the top-$n$ resulting list if the top-$n$
list covers both faulty predicates, and one of the faulty predicates
is ranked at the $n$ position. As seen, in \code{SchoolMate},
\tool{}'s multi-fault algorithm performed better than the single-fault
algorithm. Overall, 60\% of mutants have their faults detected in the
top-2 list, and \tool{}'s top-3 list covers both seeded faults for
84\% of mutant programs.

\noindent {\bf Time Efficiency.} In our experiments, we also
measured running time for the localization of each faulty
program. Each run took less than 1s without counting database
accessing time.

%84\% of the faults.

%In our implementation, we chose $Sus$ to be the Tarantula metric~\cite{tarantula05}. $Sus$ can be any other suspiciousness metric used in existing coverage-based statistical fault localization methods.
%Threshold $\sigma$ = ?

