\subsection{Localizing a Faulty Predicate}

%s with a Single Fault}

\begin{table}
    \footnotesize
    \setlength{\tabcolsep}{1.5pt}
    \centering
    \caption{\tool{}'s fault localization using predicate switching}\label{tab:predicate-table}
\begin{tabular}{clllcccc}
  \addlinespace
  \toprule
  \textbf{Row} & \textbf{P1} & \textbf{P2} & \textbf{P3} & \textbf{P1 AND } & \textbf{Act.} & \textbf{Exp.} & \textbf{Passed/} \\
  &    &   &   & {\bf P2 OR P3}  &  {\bf Output} & {\bf Output} & {\bf Failed}\\ 
  \midrule
  1 & False ($\times$) & True & False ($\times$) & False & (none) & Alice & Failed \\
  2 & False & False & True ($\times$) & True & Bob & (none) & Failed \\
  3 & True & True & True & True & Carol & Carol & Passed \\
  4 & True & False ($\times$) & False ($\times$) & False & (none) & Daniel & Failed \\
  \midrule
  $R$ score & 1 & 1 & 3 \\
  \bottomrule
  \addlinespace
  \multicolumn{8}{l}{P1: Age $>$= 25 \hspace{1em} P2: Gender = `Female' \hspace{1em} P3: Country $<>$ `USA'}
\end{tabular}
\end{table}

%\begin{table*}
%    \footnotesize
%    \centering
%    \caption{Illustration of \tool{}'s fault localization using predicate switching}\label{tab:predicate-table}
%\begin{tabular}{clllcccc}
%  \addlinespace
%  \toprule
%  \textbf{Row} & \textbf{P1} & \textbf{P2} & \textbf{P3} & \textbf{P1 AND P2 OR P3} & \textbf{Act. Output} & \textbf{Exp. Output} & \textbf{Passed/Failed} \\
%  \midrule
%  1 & False ($\times$) & True & False ($\times$) & False & (none) & Alice & Failed \\
%  2 & False & False & True ($\times$) & True & Bob & (none) & Failed \\
%  3 & True & True & True & True & Carol & Carol & Passed \\
%  4 & True & False ($\times$) & False ($\times$) & False & (none) & Daniel & Failed \\
%  \midrule
%  $R$ score & 1 & 1 & 3 \\
%  \bottomrule
%  \addlinespace
%  \multicolumn{8}{l}{P1: Age $>$= 25 \hspace{1em} P2: Gender = `Female' \hspace{1em} P3: Country $<>$ `USA'}
%\end{tabular}
%\end{table*}

Let us explain our technique to localize a faulty predicate and
then our generalization to support the localizing of multiple faulty
ones.  The technique for localizing a single faulty predicate is used
only internally by {\tool}, while the general algorithm is for localizing
any numbers of faulty predicates. Table~\ref{tab:predicate-table}
(called a \emph{predicate table}) illustrates our predicate switching
technique to localize the faulty predicate for the running example.
% in Section 2.
%, assuming that there is \emph{a single fault} in the SQL query. 
The predicate table contains the evaluation results of individual
(atomic) predicates in the \query{WHERE} clause. This information is
recorded at run time as the instrumented PHP interpreter evaluates the
predicates in the
\query{WHERE} condition (see Section 3.1). In
Table~\ref{tab:predicate-table}, the three predicates \code{Age $>$=
25}, \code{Gender = `Female'}, and \code{Country $<>$ `USA'} are denoted
by \code{P1}, \code{P2}, and {P3}, respectively. As seen, the
\query{WHERE} expression (\code{P1 AND P2 OR P3}) for rows 2 and 3
evaluates to \code{True}, thus the execution returns
\code{Bob} and \code{Carol} (column \code{Act. Output}). In contrast,
the \query{WHERE} expression for rows 1 and 4 evaluates to
\code{False}, thus \code{Alice} and \code{Daniel} are not included in
the returned result. The columns \code{Exp. Output} and
\code{Passed/Failed} show the expected output and the passed/failed
status of the corresponding row-based test case.

%If the actual output (column \code{Act. Output}) is the same as the expected output (column \code{Exp. Output}), the corresponding row (test case) will be marked as \code{Passed}; otherwise, it will be marked as \code{Failed} (column \code{Passed/Failed}).

Given the table row of a \emph{failed} test case, \tool{} attempts to
switch the current boolean value for one predicate at a time and
re-evaluates the \query{WHERE} clause with the predicate's new
value. If the value of the \query{WHERE} clause changes (from
\code{True} to \code{False} or vice versa), meaning that the given row
is now a \emph{passed} test case, \tool{} records this event to
compute the likelihood that the predicate contains a fault. In
Table~\ref{tab:predicate-table}, those predicates and their
corresponding rows are marked with the notation $\times$. In the first
row, if either \code{P1} or \code{P3} is switched from \code{False} to
\code{True}, the value of the
\query{WHERE} condition \code{P1 AND P2 OR P3} will change to
\code{True}, and therefore \code{Alice} will be output as expected. 
In contrast, changing the value of \code{P2} from \code{True} to
\code{False} does not affect the original output result. After
applying predicate switching to all predicates and table rows,
\tool{} computes the suspiciousness score $R$ for a predicate by
summing up the total of times its switched value changes a failed test
case~to a passed one. In Table~\ref{tab:predicate-table}, \code{P3}'s
$R$ score is 3 whereas \code{P1} and \code{P2}'s scores are 1.
Thus, the predicate having the highest suspiciousness score
(\code{P3}) is the one likely containing the fault.

%Therefore, the real fault at the predicate \code{P3} can be localized using the \tool{}'s predicate switching technique.

%\begin{figure}[t]
%    \centering
%\begin{lstlisting} [
%    emph={foreach, in, if, then},
%	mathescape=true,
%    xleftmargin=11pt
%]
%$R(P_i) \leftarrow 0, \forall $ Predicate $P_i$ in $WhereExp$
%foreach Failed Test Case $R$
%    foreach Predicate $P_i$ in $WhereExp$
%        $P_i(R)$.switchBooleanValue() // $P_i(R)$ = NOT $P_i(R)$
%        result $\leftarrow$ evaluateExp($WhereExp$, $R$)
%        if result = ExpectedResult($WhereExp$, $R$) then
%            $R(P_i)$ = $R(P_i)$ + 1
%        $P_i(R)$.restoreBooleanValue()
%\end{lstlisting}
%    \caption{Predicate switching algorithm to localize single predicate faults}\label{fig:algorithm-singfaults}
%\end{figure}
%
%Figure~\ref{fig:algorithm-singfaults} summarizes \tool{}'s predicate switching technique to localize the fault in a predicate of an SQL query. For each failed test case $R$ and a predicate $P_i$, \tool{} first switches the current value of $P_i$ at row $R$ (line 4) and re-evaluates the \query{WHERE} expression (line 5). If the value of the \query{WHERE} expression after switching is the same as the expected result for row $R$, \tool{} increases the $R$ score of $P_i$ by one (lines 6-7). The value of $P_i(R)$ will then be restored to its original value before \tool{} repeats the same process on other predicates and rows (line 8).


%%To show the usefulness of \tool{}'s predicate switching technique, 
Let us provide the following theorems to give the theoretical evidence
that for an SQL query with a single predicate fault, the faulty
predicate always has the highest suspiciousness score; moreover, given
sufficient test cases, its score is at least double the scores of
other predicates.

\begin{theorem}
\label{thm1}
{\em Let $P_1$, $P_2$, \ldots, $P_n$ be the predicates in the \query{WHERE}
expression of an SQL query. Suppose that there is a single fault in
one of the predicates, namely $P_*$, then $R(P_*) \ge R(P_i), \forall
i = 1 \ldots n$ and $P_i \neq P_*$.}
\end{theorem}

\begin{proof}
Let $m$ be the number of failed test cases in the predicate table. For
a failed test case, switching the value of the faulty predicate $P_*$
makes the test case passed, since the failed test case is caused by
the fault in $P_*$. Thus, the $R$ score for $P_*$ is increased by
one for every failed test case. Overall, the score of
$P_*$ is $R(P_*) = m$ (1). In contrast, changing the values of other
predicates may or may not affect the original outcome since they are
not the real cause of the error. Thus, the $R$ score of a non-faulty
predicate is either not increased or increased by one for every failed
test case. It follows that $R(P_i) \le m, \forall i = 1 \ldots n$ and
$P_i \neq P_*$ (2). From (1) and (2), we have $R(P_*) \ge
R(P_i), \forall i = 1 \ldots n$ and $P_i \neq P_*$.
\end{proof}

\input{solution-predicatefaults-proof} 